A multi-species benchmark for training and validating mass spectrometry proteomics machine learning models

### 2024-09-30 doc/nine-species/nine-species.tex
Added citations to table 1

\begin{table}
  \centering
  \scriptsize
\begin{tabular}{lllrrrrrrrrrr}
\hline
PRIDE & Species & UniProt & Files & Spectra &
\multicolumn{2}{c}{Main} & \multicolumn{2}{c}{Balanced} & Pre & Frag \\
& & & & & PSM & Pep  & PSM & Pep  \\
\hline
PXD005025 & \textit{Vigna mungo} & UP000087766 & 24 & 932,848 &
\edit{108,402} & \edit{11,638} & \edit{102,255} & \edit{11,557}
& 20 & 0.05 \\
PXD004948 & \textit{Mus musculus} & UP000000589 & 13 & 306,786 & 
\edit{25,522} & \edit{5630} & \edit{25,522} & \edit{5630}
& 10 & 0.05 \\
PXD004325 & \textit{Methanosarcina mazei} & UP000033058  & 72 & 3,728,183 &
\edit{267,183} & \edit{15,220} & \edit{100,485} & \edit{11,934}
& 10 & 0.05 \\
PXD004565 & \textit{Bacillus subtilis} & UP000001570 & 106 & 4,336,428 &
\edit{1,351,938} & \edit{28,364} & \edit{113,234} & \edit{17,481}
& 30 & 0.05 \\
PXD004536 & \textit{Candidatus endoloripes} & UP000094849 & 11 & 2,272,023 &
\edit{82,514} & \edit{8080} & \edit{82,514} & \edit{8080}
& 20 & 0.05 \\
PXD004947 & \textit{Solanum lycopersicum} & UP000004994 & 60 & 603,506 &
\edit{177,553} & \edit{48,459} & \edit{100,056} & \edit{35,787}
& 15 & 0.05 \\
PXD003868 & \textit{Saccharomyces-cerevisiae} & UP000002311 & 27 & 1,477,397 &
\edit{585,846} & \edit{19,102} & \edit{108,973} & \edit{13,285}
& 20 & 0.05 \\
PXD004467 & \textit{Apis mellifera} & UP000005203 & 17 & 823,169 &
\edit{194,604} & \edit{21,081} & \edit{102,285} & \edit{18,630}
& 20 & 0.05 \\
PXD004424 & \textit{H.\ sapiens} & UP000005640 & 26 & 684,821 &
\edit{44,555} & \edit{10,848} & \edit{44,555} & \edit{10,848}
& 20 & 0.02 \\
\hline
Total & & & 343 & 15,165,161  & \edit{2,838,117} & \edit{168,422} & \edit{779,879} & \edit{133,232} \\
\end{tabular}
\caption{{\bf Two versions of the nine-species benchmark.}
  Counts of the number of annotated spectra and distinct peptide sequences are provided for the main and balanced versions of the benchmark.
The final two columns specify the precursor window size (in ppm) and fragment bin size (in Da) used in the database search step.
}
\label{tab:benchmark}
\end{table}

@@

We downloaded the RAW files from the corresponding PRIDE projects (Table~\ref{tab:benchmark}) and converted them to MGF format using the ThermoRawFileParser v1.3.4.
We downloaded the corresponding nine UniProt reference proteomes and constructed a Tide index for each one, using Crux version 4.2.
Note that, for one species (\textit{Vigna mungo}) no reference proteome is available, so we used the proteome of the closely related species \textit{Vigna radiata}.

>>>>

\begin{table}
  \centering
  \scriptsize
\begin{tabular}{lllrrrrrrrrrr}
\hline
PRIDE & Species & UniProt & Files & Spectra &
\multicolumn{2}{c}{Main} & \multicolumn{2}{c}{Balanced} & Pre & Frag \\
& & & & & PSM & Pep  & PSM & Pep  \\
\hline
PXD005025 \cite{paiva2016label} & \textit{Vigna mungo} & UP000087766 & 24 & 932,848 &
\edit{108,402} & \edit{11,638} & \edit{102,255} & \edit{11,557}
& 20 & 0.05 \\
PXD004948 \cite{nevo2017impact} & \textit{Mus musculus} & UP000000589 & 13 & 306,786 & 
\edit{25,522} & \edit{5630} & \edit{25,522} & \edit{5630}
& 10 & 0.05 \\
PXD004325 \cite{cassidy2016combination} & \textit{Methanosarcina mazei} & UP000033058  & 72 & 3,728,183 &
\edit{267,183} & \edit{15,220} & \edit{100,485} & \edit{11,934}
& 10 & 0.05 \\
PXD004565 \cite{reuss2017large} & \textit{Bacillus subtilis} & UP000001570 & 106 & 4,336,428 &
\edit{1,351,938} & \edit{28,364} & \edit{113,234} & \edit{17,481}
& 30 & 0.05 \\
PXD004536 \cite{petersen2016chemosynthetic} & \textit{Candidatus endoloripes} & UP000094849 & 11 & 2,272,023 &
\edit{82,514} & \edit{8080} & \edit{82,514} & \edit{8080}
& 20 & 0.05 \\
PXD004947 \cite{mata2017depth} & \textit{Solanum lycopersicum} & UP000004994 & 60 & 603,506 &
\edit{177,553} & \edit{48,459} & \edit{100,056} & \edit{35,787}
& 15 & 0.05 \\
PXD003868 \cite{seidel2017quantitative} & \textit{Saccharomyces-cerevisiae} & UP000002311 & 27 & 1,477,397 &
\edit{585,846} & \edit{19,102} & \edit{108,973} & \edit{13,285}
& 20 & 0.05 \\
PXD004467 \cite{hu2016proteome} & \textit{Apis mellifera} & UP000005203 & 17 & 823,169 &
\edit{194,604} & \edit{21,081} & \edit{102,285} & \edit{18,630}
& 20 & 0.05 \\
PXD004424 \cite{cypryk2017proteomic} & \textit{H.\ sapiens} & UP000005640 & 26 & 684,821 &
\edit{44,555} & \edit{10,848} & \edit{44,555} & \edit{10,848}
& 20 & 0.02 \\
\hline
Total & & & 343 & 15,165,161  & \edit{2,838,117} & \edit{168,422} & \edit{779,879} & \edit{133,232} \\
\end{tabular}
\caption{{\bf Two versions of the nine-species benchmark.}
  Counts of the number of annotated spectra and distinct peptide sequences are provided for the main and balanced versions of the benchmark.
The final two columns specify the precursor window size (in ppm) and fragment bin size (in Da) used in the database search step.
}
\label{tab:benchmark}
\end{table}

@@

We downloaded the RAW files from the corresponding PRIDE projects (Table~\ref{tab:benchmark}) and converted them to MGF format using the ThermoRawFileParser v1.3.4 \cite{hulstaert:thermorawfileparser}.
We downloaded the corresponding nine UniProt reference proteomes and constructed a Tide index for each one, using Crux version 4.2.
Note that, for one species (\textit{Vigna mungo}) no reference proteome is available, so we used the proteome of the closely related species \textit{Vigna radiata}.
